Formatting Instructions for NIPS 2014

### 2014-04-23 paper/paper.tex
Explain raw data processing in paper

First, we need to create labeled data to use in training our models.
We use two strategies to do this.

\subsection{Strategy 1}
We sort the data set in increasing time.
For each line, we define $\delta$, the future change in stock price, to be the current stock price subtracted from the next stock price in the future.
We will attempt to build a model which calculates $\delta_t$ when given $P_t$, the values of the 26 parameters at time $t$.

>>>>

First, we create labeled data to use in training our models using the following process:
We sort the data set in increasing time.
For each line, we define $\delta$, the difference in stock price after 2 minutes, to be the current stock price subtracted from the stock price that is associated with the datapoint that is closest to 2 minutes in the future.
(Note that our datapoints are roughly 50 milliseconds apart, so we can expect that the variation in distance between sets of data points will be much less than modeling error.)
We will attempt to build a model which calculates $\delta_t$ when given $P_t$, the values of the 26 parameters at time $t$.
